Retrofitting Effect Handlers onto OCaml

### 2021-03-13 retro-concurrency.tex
very minor proof-reading edits to the introduction

Many programming languages, including OCaml, require non-local change to the
code in order to support asynchronous I/O, often leading to a dichotomy
synchronous and asynchronous code~\cite{colour}. Since OCaml does not have
primitive support for concurrency, users will have to use monadic I/O libraries
such as Lwt~\cite{lwt} and Async~\cite{async}, where all asynchronous code must
use monad syntax. Languages such as GHC Haskell and Go provide lightweight
threads, which avoids the dichotomy between synchronous and asynchronous code.
However, these languages bake-in the lightweight thread implementation into the
runtime system. With effect handlers, asynchronous I/O can be implemented
directly in OCaml as a library.

In order to support forking and yielding threads, we declare effects the
following effects:

@@

The |Fork| effect takes a thunk which is spawned as a concurrent thread, and
|Yield| yields control to another thread in the scheduler queue. We can define
helper functions to perform these effects:

>>>>

Many programming languages, including OCaml, require non-local change to the
code in order to support asynchronous I/O, often leading to a dichotomy between
synchronous and asynchronous code~\cite{colour}. Since OCaml does not have
primitive support for concurrency, users will have to use monadic I/O libraries
such as Lwt~\cite{lwt} and Async~\cite{async}, where all asynchronous code must
use monad syntax. Languages such as GHC Haskell and Go provide lightweight
threads, which avoids the dichotomy between synchronous and asynchronous code.
However, these languages bake-in the lightweight thread implementation into the
runtime system. With effect handlers, asynchronous I/O can be implemented
directly in OCaml as a library.

In order to support forking and yielding threads, we declare the
following effects:

@@

The |Fork| effect takes a thunk which is spawned as a concurrent thread, and the
|Yield| effect yields control to another thread in the scheduler queue. We can define
helper functions to perform these effects:
